Kimbee: A Speech Therapy Application For Children

### 2015-03-09 Paper/paper.tex
Figure Fixing

\numberofauthors{1}
\author{
    \alignauthor
    \vspace*{-0.3in}
        Ryan Drapeau \hspace{3.0cm}
        Nick Huynh \hspace{3.0cm}
        Aaron Nech \\
    \affaddr{
        \hspace{0.3cm}
        University of Washington \hspace{1.4cm}
        University of Washington \hspace{1.4cm}
        University of Washington \hspace{0cm}
        } \\[7 pt]
    \email{{\centering \{drapeau, huynick, necha\}@cs.washington.edu}}
}

@@

\subsection{Game ({\secit Kimbee})}

\subsection{Therapist Portal}

@@

@@

There are a few ways that we can expand on {\em Kimbee}. We plan on deploying the project for use in the Arlington Public School District to see how children respond and learn from {\em Kimbee} along with how experienced speech therapists use {\em Kimbee} to aid the therapy process. Along with this, we can also expand on the application itself by targeting speech sounds past the `R' and `W' sound replacement. We can also enhance the child's experience by adding more mini games for the child to play and a token system for children to spend the honey they collect on aesthetics for the bee character.

>>>>

\numberofauthors{1}
\author{
    \alignauthor
    \vspace*{-0.3in}
        Ryan Drapeau \hspace{3.0cm}
        Nick Huynh \hspace{3.0cm}
        Aaron Nech \\
    \affaddr{
        \hspace{0.3cm}
        University of Washington \hspace{1.4cm}
        University of Washington \hspace{1.4cm}
        University of Washington \hspace{0cm}
        } \\[3 pt]
    \email{{\centering \{drapeau, huynick, necha\}@cs.washington.edu}}
}

@@

\begin{figure*}[t]
  \centering
  \includegraphics[keepaspectratio, width=\textwidth]{user_figure.png}
  \vspace{-26 pt}
  \caption{\normalfont Left: The flow diagram showing how therapists and children exchange data. Right: The game interface.}
  \label{fig:user}
\end{figure*}

\subsection{User Flow}

We will first describe the flow a typical user would take when using this application. The flow is split into two parts, one to describe the game the child or user would play and another to describe what the therapist would see.

\subsubsection{Game (Kimbee)}

[User Flow Game Here]

\subsubsection{Therapist Portal}

[User Flow Therapist Portal Here]

\begin{figure*}[t]
  \centering
  \includegraphics[keepaspectratio, width=\textwidth]{tech_figure.png}
  \caption{Left: AAA. Middle: BBB. Right: CCC.}
  \label{fig:tech}
\end{figure*}

\subsection{Implementation Details}

We will now discuss the implementation details of each of the systems that make up {\em Kimbee}.

\subsubsection{Game (Kimbee)}

[Game Implementation Details Here]

\subsubsection{Therapist Portal}

[Therapist Portal Implementation Details Here]

@@

[Results Here]

There are a few ways that we can expand on {\em Kimbee}. We plan on deploying the project for use in the Arlington Public School District to see how children respond and learn from {\em Kimbee} along with how experienced speech therapists use {\em Kimbee} to aid the therapy process. Along with this, we can also expand on the application itself by targeting speech sounds past the `R' and `W' sound replacement. We can also enhance the child's experience by adding more mini-games for the child to play and a token system for children to spend the honey they collect on aesthetics for the bee character.

@@

[Conclusion Here]
